---
title: "Sustainable Intensification"
output:
  word_document: default
  html_notebook: default
  html_document:
    df_print: paged
---
## SQ1: Is farming with Silvopastoral Systems in Caquetá a from of Sustainable Intensification?  

```{r, message=FALSE}
library(tidyverse) # loading R packages
library(ggplot2)
load("Dataframes/si.df.rda") # Load Dataframe
si.df <- filter(si.df, land_type=="Lomerío (lomas, mesas y vallecitos" & SPS!="NA") # filtering data to only contain farms on landscape "hills" and missing responses for SPS
```

### Creating Scatterplotts
```{r}
ggplot(data = si.df)+
  geom_point(mapping = aes(x=milkperhectare, y= distance, colour=SPS))
ggplot(data = si.df)+
  geom_point(mapping = aes(x=labourperhectare, y= stocking_rate, colour=SPS))
```

**Stocking rates**

### Histograms and Q-Q plots for stocking rates of farmers without and with SPS 
```{r}
par(mfrow=c(2,2))
hist(si.df$stocking_rate[si.df$SPS==FALSE],breaks = 60, main="farmers without SPS")
qqnorm(si.df$stocking_rate[si.df$SPS==FALSE], ylim = c(0,6))
qqline(si.df$stocking_rate[si.df$SPS==FALSE], ylim = c(0,6))
hist(si.df$stocking_rate[si.df$SPS==TRUE],breaks = 15, main="farmers with SPS")
qqnorm(si.df$stocking_rate[si.df$SPS==TRUE], ylim = c(0,6))
qqline(si.df$stocking_rate[si.df$SPS==TRUE], ylim = c(0,6))
```

### Log-transformation of stocking rates
```{r}
si.df$stocking_rate.log <- log(si.df$stocking_rate)
```

### Histograms and Q-Q plots of log-stocking rates
```{r}
par(mfrow=c(2,2))
hist(si.df$stocking_rate.log[si.df$SPS==FALSE], breaks = 60, main = "farmers without SPS")
qqnorm(si.df$stocking_rate.log[si.df$SPS==FALSE], ylim = c(-3,3))
qqline(si.df$stocking_rate.log[si.df$SPS==FALSE], ylim = c(-3,3))
hist(si.df$stocking_rate.log[si.df$SPS==TRUE], breaks = 15, main="farmers with SPS")
qqnorm(si.df$stocking_rate.log[si.df$SPS==TRUE], ylim = c(-3,3))
qqline(si.df$stocking_rate.log[si.df$SPS==TRUE], ylim = c(-3,3))
```

### Boxplots of stocking rates of farmers without and with SPS
```{r}
ggplot(data=si.df)+
  geom_boxplot(mapping = aes(y=stocking_rate.log, x=SPS))
```

### Two-sided t-test of means of log-stocking rates of farmers without and with SPS
```{r}
stock.t_test <- t.test(
  x=si.df$stocking_rate.log [si.df$SPS==FALSE],
  y=si.df$stocking_rate.log [si.df$SPS==TRUE])
stock.t_test
```

### Transformation of means of log-stocking rates back to level
```{r}
exp(stock.t_test$estimate)
```
Conventional farmers have a mean stocking rate of `r exp(stock.t_test$estimate[1])`. SPS farmers have a mean stocking rate of `r exp(stock.t_test$estimate[2])`. Even though the mean stocking rates (geometric means) of SPS farmers are higher they don't differ significantly. The Null-hypotheses (both means are the same) can not be rejected.

**Annual milk yield per hectare**

### Histograms and Q-Q plots of milk yields of farmers without and with SPS
```{r}
par(mfrow=c(2,2))
hist(si.df$milkperhectare[si.df$SPS==FALSE],breaks = 70, main="farmers without SPS")
qqnorm(si.df$milkperhectare[si.df$SPS==FALSE], ylim = c(-0,2500))
qqline(si.df$milkperhectare[si.df$SPS==FALSE], ylim = c(-0,2500))
hist(si.df$milkperhectare[si.df$SPS==TRUE],breaks = 15, main="farmers with SPS")
qqnorm(si.df$milkperhectare[si.df$SPS==TRUE], ylim = c(-0,2500))
qqline(si.df$milkperhectare[si.df$SPS==TRUE], ylim = c(-0,2500))
```

### Log-transformation of milk yields
```{r}
si.df$milkperhectare.log <- log(si.df$milkperhectare)
```

### Histograms and Q-Q plots of log-milk yields
```{r}
par(mfrow=c(2,2))
hist(si.df$milkperhectare.log[si.df$SPS==FALSE], breaks = 70, main = "farmers without SPS")
qqnorm(si.df$milkperhectare.log[si.df$SPS==FALSE], ylim = c(4,8))
qqline(si.df$milkperhectare.log[si.df$SPS==FALSE], ylim = c(4,8))
hist(si.df$milkperhectare.log[si.df$SPS==TRUE], breaks = 15, main="farmers with SPS")
qqnorm(si.df$milkperhectare.log[si.df$SPS==TRUE], ylim = c(4,8))
qqline(si.df$milkperhectare.log[si.df$SPS==TRUE], ylim = c(4,8))
```

### Boxplots of  log milk yield
```{r}
ggplot(data=si.df)+
  geom_boxplot(mapping = aes(y=milkperhectare.log, x=SPS))
```

### T-test comparing mean milk yields per hectare of farmers with and without SPS
```{r}
my.t_test <- t.test(
  x=si.df$milkperhectare.log[si.df$SPS==FALSE],
  y=si.df$milkperhectare.log[si.df$SPS==TRUE])
my.t_test
```

### Transformation of means of log-milk yields back to level
```{r}
exp(my.t_test$estimate)
```
The two-sided t-test shows a higher annual mean milk yield per hectare for SPS farmers. However results are not significant as the Null-hypothesis cannot be rejected. 

**Annual labour days per hectare**  

### Histograms and Q-Q plot of labour days of farmers without and with SPS
```{r, echo=FALSE}
par(mfrow=c(2,2))
hist(si.df$labourperhectare[si.df$SPS==FALSE],breaks = 83, main="farmers without SPS")
qqnorm(si.df$labourperhectare[si.df$SPS==FALSE], ylim = c(-0,40))
qqline(si.df$labourperhectare[si.df$SPS==FALSE], ylim = c(-0,40))
hist(si.df$labourperhectare[si.df$SPS==TRUE],breaks = 83, main="farmers with SPS")
qqnorm(si.df$labourperhectare[si.df$SPS==TRUE], ylim = c(-0,40))
qqline(si.df$labourperhectare[si.df$SPS==TRUE], ylim = c(-0,40))
```

### Log-transformation of labour days
```{r}
si.df$labourperhectare.log <- log(si.df$labourperhectare+0.01)
```

### Histograms and Q-Q plots of log-labour days
```{r, echo=FALSE}
par(mfrow=c(2,2))
hist(si.df$labourperhectare.log[si.df$SPS==FALSE], breaks = 70, main = "farmers without SPS")
qqnorm(si.df$labourperhectare.log[si.df$SPS==FALSE], ylim = c(-4,4))
qqline(si.df$labourperhectare.log[si.df$SPS==FALSE], ylim = c(-4,4))
hist(si.df$labourperhectare.log[si.df$SPS==TRUE], breaks = 15, main="farmers with SPS")
qqnorm(si.df$labourperhectare.log[si.df$SPS==TRUE], ylim = c(-4,4))
qqline(si.df$labourperhectare.log[si.df$SPS==TRUE], ylim = c(-4,4))
```

### Boxplot of labour days
```{r, echo=FALSE}
ggplot(data=si.df)+
  geom_boxplot(mapping = aes(y=labourperhectare.log, x=SPS))
```

### T-test comparing mean labour hours per hectare of farmers without and with SPS
```{r}
lh.t_test <- t.test(
  x=si.df$labourperhectare.log[si.df$SPS==FALSE],
  y=si.df$labourperhectare.log[si.df$SPS==TRUE])
lh.t_test
```

### Transformation of means of log-labour days back to level
```{r}
exp(lh.t_test$estimate)-0.01
```
Mean annual labour days per hectare are slightly higher for SPS farmers than for conventional farmers. The difference however is not significantly high enough to reject the NUll-hypothesis of both means beeing equal.

**Distance to highway**

### Histograms and Q-Q plots of distance of farmers without and with SPS
```{r}
par(mfrow=c(2,2))
hist(si.df$distance[si.df$SPS==FALSE],breaks = 70, main="farmers without SPS")
qqnorm(si.df$distance[si.df$SPS==FALSE], ylim = c(-0,25000))
qqline(si.df$distance[si.df$SPS==FALSE], ylim = c(-0,25000))
hist(si.df$distance[si.df$SPS==TRUE],breaks = 15, main="farmers with SPS")
qqnorm(si.df$distance[si.df$SPS==TRUE], ylim = c(-0,25000))
qqline(si.df$distance[si.df$SPS==TRUE], ylim = c(-0,25000))
```

### Boxplots of distance
```{r}
ggplot(data=si.df)+
  geom_boxplot(mapping = aes(y=distance, x=SPS))
```

### T-test comparing mean distance of farmers without and with SPS
```{r}
d.t_test <- t.test(
  x=si.df$distance[si.df$SPS==FALSE],
  y=si.df$distance[si.df$SPS==TRUE])
d.t_test
```
The mean distance indicates that SPS farmers are located a little further from the highway. Again however the difference is not significant enough to reject the Null-hypothesis that both means are the same. 

```{r, echo=FALSE}
save(si.df, file = "Dataframes/si.df.rda")
```

