---
title: "FilteringSilvopastoralfarmers"
output: html_notebook
---



*installing tidyverse*
```{r}
library(tidyverse)
```

###Filtering for Farmers that practice Silvopastorilfarming but don't have Cattle
```{r}
head(filter(Farmers, Silvopastoril =='yes', Farmers$Cattleranching=='False'))
```

Why do three Farmers say they have Silvopastoral Areas but don't say they practice Milk or Meatproduction?

```{r}
filter(Farmers, Silvopastoril =='yes', Farmers$Cattleranching=='False')[,23:29]
```
All three farmers have Cows, however for two of them we don't know whether they are in production. We can assert that all of them are also Cattleranchers.
```{r}
filter(Farmers, Silvopastoril =='yes', Farmers$Cattleranching=='False')[,9]
```
All three have land in pasture.
```{r}
filter(Farmers, Silvopastoril =='yes', Farmers$Cattleranching=='False')[,30:32]

```
Because two of them have unknown values for Cows we don't know their StockingRate. Possible solution is to assume that NAs in COW are actually `r '0'`animals. 


