---
title: "Log Transformation"
output: html_notebook
---
Load Dataframe
```{r}
load("Dataframes/si.df.rda")
```

Summary of si.df
```{r}
summary(si.df)
```

Historgrams of au and area_total

```{r}
apply(si.df[,2:3], 2, hist, breaks=100)
```
Au and area_total area skewed to the right

Point cloud of AU and area_total
```{r}
library(ggplot2)
ggplot(data=si.df)+
  geom_point(mapping = aes(au, area_total))
```

Log transformation:
```{r}
si.df$au.log <- log(si.df$au)
si.df$area_total.log <- log(si.df$area_total)
```
Histogram of Logs of AU and area_total
```{r}
apply(si.df[,41:42], 2, hist, breaks=100)
```

Results look much more normally distribuited. 

Point cloud of AU.log and area_total.log
```{r}
library(ggplot2)
ggplot(data=si.df)+
  geom_point(mapping = aes(au.log, area_total.log))
```
Simple regression of AU and area_total
```{r}
sl <-(lm(au~area_total, data=si.df))
plot(sl)
plot(si.df$area_total, rstandard(sl))
```
With each hectare farmers add 0.2 au. Five hectares add one au.

simple linear regression of au.log and area_total.log

```{r}
sllog <- lm(au.log~area_total.log, data = si.df)
plot(sllog)
plot(si.df$area_total.log, rstandard(sllog))
```
Model loses significance, R is much lower
```{r}
hist(sl$residuals)
hist(sllog$residuals)
```
QQ Plots
```{r}
qqnorm(sl$residuals)
qqline(sl$residuals)
```

QQ Plots log
```{r}
qqnorm(sllog$residuals)
qqline(sllog$residuals)

```
Box Cox
```{r}
library(MASS)
bx <- boxcox(sl)
best.lam <- bx$x[which(bx$y==max(bx$y))]
```
Regression of lambda transformation
```{r}
slbx <- lm(au^best.lam ~ area_total, data = si.df)
plot(slbx)
summary(sl)
summary(slbx)
```

