---
title: "Mahalanobis Outliers"
output:
  word_document: default
  html_notebook: default
---
```{r echo = FALSE, results='hide'}
library(tidyverse)
library(ggplot2)
load("Dataframes/si.df.rda")
si.df <-  si.df[is.finite(si.df[,40]),] # Filter elements with TFP is INF
si.df <- filter(si.df, au!="NA" , forest_reserves!="NA") # Filter elements where au and forest_reserves are NA
summary(si.df)
```
## Removeing Outliers using the Mahalanobis distance

Find Outliers using Mahalanobis distance of "distance" ,"stocking_rate", "forest_reserves", "labourperhectare", "milkperhectare", "tfp". Mahalanobis distance calculates the standard Euclidean distance of each point to the mean. It is unitless, scale-invariant and includes correlations (Wikipedia!! Scite correctly)

```{r}
df <- c(14,32,12,36,37,40) #"distance" ,"stocking_rate", "forest_reserves", "labourperhectare", "milkperhectare", "tfp"

summary(si.df[df])
si.mhlnbs_outl <- mahalanobis(si.df[,df],colMeans(si.df[,df]),cov(si.df[,df]))
si.mhlnbs_outl # Calculated Mahalanobis distances
```

Add Mahalanobis distance to dataframe si.df
```{r}
si.df$mhlnbs <- round(si.mhlnbs_outl,3)
summary(si.df$mhlnbs)
#save(si.df, file = "Dataframes/si.df.rda")
```

Boxplot Statistics of Mahalanobis distance
```{r}
boxplot.stats(si.df$mhlnbs)
boxplot(si.df$mhlnbs)
```

The boxplot identifies a Mahalanobis distance of bigger than 8.3 as outlier.


Create binomial variable of Mahalanobis Outliers, level 8.3 is chosen
```{r}
outlier <- 8.3
si.df$outlier_mhlnbs <- ifelse(si.df$mhlnbs > outlier, TRUE, FALSE)
summary(si.df$outlier_mhlnbs)
```

12 outliers are identified

Visualize Outliers - Point clouds, above are SPS=FALSE, below SPS=TRUE. y axis displays Mahalanobis distance, the horizontal line shows the 14 boundary. 
```{r}
ggplot(data = si.df)+
  geom_point(mapping = aes(x=mhlnbs, y= milkperhectare, size=stocking_rate, alpha=forest_reserves))+
  geom_vline(xintercept = outlier)+
  facet_wrap(~SPS, dir = "v")+
   coord_flip()

ggplot(data = si.df)+
  geom_point(mapping = aes(x=mhlnbs, y= tfp, size=stocking_rate, alpha=forest_reserves))+
  geom_vline(xintercept = outlier)+
  facet_wrap(~SPS, dir = "v")+
   coord_flip()
ggplot(data = si.df,mapping = aes(x=mhlnbs, y= labourperhectare, size=stocking_rate, alpha=forest_reserves ))+
  geom_point()+
  geom_vline(xintercept = outlier)+
  facet_wrap(~SPS, dir = "v")+
  coord_flip()
```

Build subset without Mahalanobis Outliers
```{r}
si.mhlnbsoutl <- filter(si.df, outlier_mhlnbs==FALSE)
save(si.mhlnbsoutl, file="Dataframes/si.mhlnbsoutl.rda" )
```

Boxplot Statistics of Mahalanobis distance
```{r}
boxplot.stats(si.mhlnbsoutl$mhlnbs)
boxplot(si.mhlnbsoutl$mhlnbs)
```