---
title: "SQ2"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
  html_document:
    df_print: paged
---
## Results of SQ2: Do farmers with more intensive systems have relatively more forest reserves?

### Loading R packages and dataframe 
```{r, message=FALSE}
library(tidyverse)
library(ggplot2)
library(psych)
library(heplots)
load("Dataframes/si.df.rda")
```

### Scatterplots, histograms and correlations of forest reserves, stocking rates, annual milk yields per hectare, annual labour days per hectare and distances to highway
```{r}
model.var <- c(12,32, 36, 37, 14) # forest_reserves,stocking rate, milkperhectare, labourperhectare, distance
pairs.panels(si.df[,model.var],
             gap=0,
             bg=c("red")[si.df$SPS],
             pch = 21)
```

### Log-transformation of forest reserves
```{r}
si.df$forest_reserves.log <- log(si.df$forest_reserves+0.01) ## +0.01 to avoid infinitifs 
```

### Scatterplots, histograms and correlations of log-forest reserves, log-stocking rates, log-annual milk yields per hectare, log-annual labour days per hectare and distances to highway
```{r}
log.var <- c(44,41:43,14) # forest_reserves.log,stocking_rate.log , milkperhectare.log, labourperhectare.log, distance
pairs.panels(si.df[,log.var],
             gap=0,
             bg=c("red", "green")[si.df$SPS],
             pch = 21)
```


### Calculating Mahalanobis distance of log-stocking rates, log-milk yields and log-labour days 
```{r}
si.df<-si.df[!is.na(si.df$forest_reserves.log),] # remove NA in forest_reserves.log
si.mhlnbs_outl <- mahalanobis(si.df[,c(41:43)],colMeans(si.df[,c(41:43)]),cov(si.df[,c(41:43)]))
# Calculated Mahalanobis distances
si.df$mhlnbs <- round(si.mhlnbs_outl,3) #Add to dataframe
```

###Q-Q plot of Mahalanobis distance and theoretic Chi-square quantiles
```{r}
qqPlot(si.df$mhlnbs, distribution = "chisq", df=3, envelope = FALSE, id=FALSE)
```

### Outlier definition as logic variable in dataframe
```{r}
outlier <- 5.5
si.df$outlier_mhlnbs <- ifelse(si.df$mhlnbs > outlier, TRUE, FALSE)
summary(si.df$outlier_mhlnbs)
```

### Key variables of identified outliers 
```{r, echo=FALSE}
select(filter(si.df, mhlnbs>outlier), c(1,8, 32,36,37, 45)) #select only id_house, SPS, stocking_rate, labourperhectare, milkperhectare, mhlnbs 
``` 

### Scatterplots of Mahalanobis distance and milk yields, labour days and stocking rates
```{r}
labs <- c("FALSE"="SPS=FALSE", "TRUE"="SPS=TRUE")
par(mfrow=c(3,1))
ggplot(data = si.df, mapping = aes(x=mhlnbs, y= milkperhectare))+
  geom_point(color="blue")+
  geom_vline(xintercept = outlier)+
  facet_wrap(~SPS, dir = "v", labeller = labeller(SPS=labs))+
   coord_flip()+
  geom_text(aes(x=mhlnbs, y= milkperhectare, label=ifelse(mhlnbs>7,as.character(id_house),'')),hjust=0,vjust=0)

ggplot(data = si.df,mapping = aes(x=mhlnbs, y= labourperhectare))+
  geom_point( color="blue")+
  geom_vline(xintercept = outlier)+
  facet_wrap(~SPS, dir = "v", labeller = labeller(SPS=labs))+
  coord_flip()+
  geom_text(aes(x=mhlnbs, y= labourperhectare, label=ifelse(mhlnbs>7,as.character(id_house),'')),hjust=0,vjust=0)

ggplot(data = si.df,mapping = aes(x=mhlnbs, y= stocking_rate))+
  geom_point( color="blue")+
  geom_vline(xintercept = outlier)+
  facet_wrap(~SPS, dir = "v", labeller = labeller(SPS=labs))+
  coord_flip()+
  geom_text(aes(x=mhlnbs, y= stocking_rate, label=ifelse(mhlnbs>7,as.character(id_house),'')),hjust=0,vjust=0)

```

### Removing outliers from dataframe
```{r}
si.df <- filter(si.df, outlier_mhlnbs==FALSE)
```

### Multiple linear regression model, dependent variable: log-forest reserves, independent variables: log-stocking-rates, log-milk yields, log-labour days, SPS, distance to highway
```{r}
fr_multi_reg <- lm(forest_reserves.log ~ stocking_rate.log+milkperhectare.log+labourperhectare.log+SPS+distance, data = si.df)
summary(fr_multi_reg)
```
### Q-Q plot of errorterms and theoretical quantiles
```{r}
qqPlot(fr_multi_reg)
```

### Variable selection by comparing AIC
```{r}
step(fr_multi_reg)
```

### AIC-optimized model, independent variables: SPS, distance to highway
```{r}
fr_sps_distance_reg <- lm(forest_reserves.log ~ SPS + distance, data = si.df)
summary(fr_sps_distance_reg)
```

### Leaving out single observations to see reflection on estimators
```{r}
head(dfbeta(fr_sps_distance_reg), n=10L)
```

### Q-Q plot of errorterms of AIC optimized linear model and theoretical quantiles
```{r}
qqPlot(fr_sps_distance_reg)
```

### Boxplots of log-forest reserves of farmers without and with SPS
```{r}
ggplot(data = si.df, mapping=aes(y=forest_reserves.log, x=SPS))+
  geom_boxplot()
```

### One-sided t-test of mean log-forest reserves of farmers without and with SPS  
```{r}
fr_ttest <- t.test(x=si.df$forest_reserves.log[si.df$SPS==FALSE],
       y=si.df$forest_reserves.log[si.df$SPS==TRUE], alternative = "greater"
       )
fr_ttest
```

### Transformation of means back to level values
```{r}
exp(fr_ttest$estimate)-0.01
```
