---
title: "filtering_silvopastoral_farmers"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---



*installing tidyverse*
#Load farmers.df
```{r}
library(tidyverse)
load("Dataframes/farmers.df.Rda")
```

###Filtering for Farmers that practice Silvopastorilfarming but don't have Cattle
```{r}
head(filter(farmers.df, silvopastoral ==TRUE, farmers.df$livestockproduction==FALSE))
```

Why do three Farmers say they have Silvopastoral Areas but don't say they practice Milk or Meatproduction?

#Filter Farmers that have Silvopasture and not Livestockproduction. Only show Animal-columns
```{r}
head(filter(farmers.df, silvopastoral ==TRUE, farmers.df$livestockproduction==FALSE)[,20:26])
```
All three farmers have Cows, however for two of them we don't know whether they are in production. We can assert that all of them are also Livestock producers.
```{r}
filter(farmers.df, silvopastoral ==TRUE, farmers.df$livestockproduction==FALSE)[,"f1_area_pasture_wo_sps"]
```
All three have land in pasture.
```{r}
filter(farmers.df, silvopastoral ==TRUE, farmers.df$livestockproduction==FALSE)[,c("stocking_rate_total", "stocking_rate_pasture",  "stocking_rate_pasture_silvo")]

```
Because two of them have unknown values for Cows we don't know their Stocking Rate. Possible solution is to assume that NAs in COW are actually `r '0'` animals. 
```{r}
head(farmers.df[,20:26])
```

The value 0 doesn't exist. So we assume, that NA=0.  

#Set NA <- 0 in animals.
```{r}

farmers.df.animals <- farmers.df[,20:26]
farmers.df.animals[is.na(farmers.df.animals)] <- 0
farmers.df[,20:26] <- farmers.df.animals
```

```{r}
head(farmers.df[,20:26])
```


#Set TRUE for LIvestockproduction in Farmers with Silvopastorals
```{r}
filter(farmers.df, silvopastoral ==TRUE, farmers.df$livestockproduction==FALSE)[, c("id_house", "livestockproduction")] #<- TRUE
```
```{r}
farmers.df[farmers.df$id_house == "E24", "livestockproduction"] <- TRUE
farmers.df[farmers.df$id_house == "G28", "livestockproduction"] <- TRUE
farmers.df[farmers.df$id_house == "I18", "livestockproduction"] <- TRUE
```

```{r}

filter(farmers.df, silvopastoral ==TRUE, farmers.df$livestockproduction==FALSE)[, c("id_house", "livestockproduction")] #<- TRUE
```
All Silvopastoral farmers are now also livestockfarmers.

```{r} 

save(farmers.df, file = "Dataframes/farmers.df.Rda")

```

